\section{Plan}

\todo{Should this be in the report?}
To be able to complete this project, the following parts needs to be done.

\begin{itemize}
	\item Studying of relevant topics such as the \textit{USB protocol}, the \textit{USB Audio Class}, 
	implementation the \textit{I2S protocol} and the \textit{STM32 Serial Audio Interface (SAI)} 
	functionality.
	%
	\item Selecting a high quality codec that can handle four input and four output channels, all 
	running at a sample rate of 48000 Hz.
	%
	\item Selecting a microprocessor that can interface with the chosen codec, and also has support for
	high speed USB. A development board for this specific microprocessor also needs to be available.
	%
	\item Designing and building of a PCB that can interface with a development board, containing a codec, 
	a display, potentiometers and a pin header for debugging the wires between the development board and 
	the codec.
	%
	\item Study the existing software modules for I2S communication and USB Audio classes. This is to make
	sure that they contain all the necessary components needed for this project \todo{Such as?}. 
	If these parts aren't present, they will need to be implemented.
	%
	\item Creating an architecture of the software layer, containing how each part of it should work and 
	the flow of information.
	%
	\item Build a software layer that follows the described architecture.
	%
	\item Create unit tests for parts of the software layer that can be feasible tested.
	%
	\item Write documentation for the software layer.
	%
	\item Create and build a final PCB that can be used without the development board.
	%
	\item Test the audio signals for the board.
\end{itemize}

A time plan for the completion of the master thesis can be found in Table \ref{table:timeplan}.
This project started at 6 July 2023, and is set to be finished at 18 October 2023.

The time plan is sectioned of in three sprints. The work that should be done in these sprints will be 
selected at the start of each sprint.

\begin{table}[]
	\caption{Time plan for the completion of the master thesis}
	\todo{I assume this shouldn't be in the final report either}
	\label{table:timeplan}
	\begin{tabular}{lll}
		\textbf{Week} & \textbf{Date} & \textbf{Part} \\
		V23 & 05 jun & Planning \\
		V24 & 12 jun & Rapport structuring + Pre study \\
		V25 & 19 jun & Pre study \\
		V26 & 26 jun & Pre study + selection of codec and devboard \\
		V27 & 03 jul & Sprint 1 \\
		V28 & 10 jun & Sprint 1 \\
		V29 & 17 jun & Sprint 1 \\
		V30 & 24 jun & Sprint 1 + Report writing and evaluation \\
		V31 & 31 jun & Sprint 2 \\
		V32 & 07 aug & Sprint 2 \\
		V33 & 14 aug & Sprint 2 + Report writing and evaluation \\
		V34 & 21 aug & Sprint 3 \\
		V35 & 28 aug & Sprint 3 \\
		V36 & 04 sep & Sprint 3 + Report writing and evaluation \\
		V37 & 11 sep & Final touches on development \\
		V38 & 18 sep & Report writing \\
		V39 & 25 sep & Report writing \\
		V40 & 02 okt & Report writing (First draft) \\
		V41 & 09 okt & Report writing
	\end{tabular}
\end{table}
