% TODO: Change introduction
\def\myquote{``This report, by its very length, defends itself against the risk of being read."\\[.5\baselineskip] Winston Churchill}

\makechapter[\myquote]{Introduction}{Introduction}{Introduction: Why do we put cats in containers?\label{introduction}}

\todo{We can add todo tags in order to know what needs to be done in the report}
\todo{Find more info about cats}

\noindent
In our modern world, where efficiency and organization play significant roles in our daily lives, it is essential to consider every aspect of our existence, including the comfort and well-being of our beloved feline companions. While the title of this paper may raise eyebrows or elicit a chuckle, it is crucial to clarify that our objective is not to advocate for confining cats to Tupperware containers. Rather, this study seeks to explore the art of creating secure and cozy spaces for cats, considering the concept of fitting cats into Tupperware containers as a metaphorical representation of creating safe havens within our homes.

Cats, with their independent and curious nature, often seek out secluded spots to rest and observe their surroundings. Therefore, understanding their instinctual need for a secure and confined space can lead us to develop innovative and practical solutions that promote their physical and emotional well-being. Tupperware containers, renowned for their sturdy construction and versatility, serve as a catalyst for this exploration, symbolizing a potential avenue for creating spaces that cater to our feline friends' natural inclinations.

This paper aims to delve into the significance of providing cats with appropriate hideouts, the factors to consider when designing such spaces, and the overall benefits that can be derived from incorporating these solutions into our homes. We will examine the physical characteristics of cats, their preferences for different types of hiding spots, and the psychological benefits they derive from having access to secure and comfortable environments.

By highlighting the importance of offering cats appropriate and well-designed spaces, we hope to deepen our understanding of their needs and strengthen the bond between humans and felines. Ultimately, this exploration encourages a thoughtful approach to pet ownership, promoting an environment where cats can thrive, feel safe, and exhibit their natural behaviors.

Let us embark on this journey together, exploring the creative ways we can cater to our feline friends' needs, all while maintaining a humane and respectful approach to their well-being.
